oREV item selection and analysis

### 2022-11-27 analysis/orev_item_selection.Rmd
prep second run
update determine size

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)
library(brms)
library(rstan)
library(loo)
library(coda)
library(testing)
library(geomtextpath)

@@

saveRDS(irt1_guess_itemloo_idxs, file = "../saves/irt1_guess_itemloo_idxs.rds")
```

@@

x <- sample(pkd, 20)
mean(x)

@@

  mean_pkd <- mean(pkd[subset])/5

	# sel <- items[subset == TRUE]
	# 
	# sub_dat <- data%>%
	#   filter(targetWord %in% sel)%>%
	#   group_by(subjID)%>%
	#   summarise(mean_sub = mean(correct))
	# 
	# cor <- cor(sub_dat$mean_sub,full$mean_full)
	# 
	# return(spacing + mean_discrim/6 + cor/3)
	return(spacing + mean_infit + mean_outfit+ var_disc_2PL +mean_pkd)
}

@@

```{r, message=F, warning=F, comment=F}
sim_rasch_test <- simulated_annealing_rasch(20)

@@

  for(j in 1:5){

  for (i in 21:30) {

@@

#determine_size <- readRDS("../saves/determine_size.rds")

determine_size%>%
  mutate(ratio = ifelse(elpd_diff == 0,0,ratio))%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value", title = "ratio = abs(elpd_diff)/(2*se_diff)")
```

@@

for (i in 1:10) {

@@

```{r}
icc1_guess_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line() +
  geom_textline(aes(label = item)) +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)
library(brms)
library(rstan)
library(loo)
library(coda)
library(testing)
#library(geomtextpath)

@@

saveRDS(irt1_guess_itemloo_idxs, file = "../saves/irt1_guess_itemloo_idxs.rds")

irt1_guess_itemloo_idxs <- readRDS(file = "../saves/irt1_guess_itemloo_idxs.rds")
```

@@

@@

  #mean_pkd <- mean(pkd[subset])/5

	# sel <- items[subset == TRUE]
	# 
	# sub_dat <- data%>%
	#   filter(targetWord %in% sel)%>%
	#   group_by(subjID)%>%
	#   summarise(mean_sub = mean(correct))
	# 
	# cor <- cor(sub_dat$mean_sub,full$mean_full)
	# 
	# return(spacing + mean_discrim/6 + cor/3)
	return(spacing + mean_infit + mean_outfit+ var_disc_2PL)
}

@@

```{r, message=F, warning=F, comment=F}
sim_rasch_test <- simulated_annealing_rasch(22)

@@

  for(j in 5:5){

  for (i in c(36:40)) {

@@

determine_size <- readRDS("../saves/determine_size.rds")

determine_size%>%
  mutate(ratio = ifelse(elpd_diff == 0,0,ratio))%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  #geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value", title = "ratio = abs(elpd_diff)/(2*se_diff)")

determine_size%>%
  group_by(size)%>%
  summarise(n())

determine_size%>%
  group_by(size)%>%
  mutate(iter = 1:n())
```

@@

for (i in 1:20) {

@@

```{r}
icc1_guess_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  geom_line() +
  #geom_textline(aes(label = item)) +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
